\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-23 paper.tex

In Fig. \ref{fig:JDR}(a) we show the current density
$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
corresponding to positions $A$, $B$, and $C$ on the samples.
In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
selected positions of both samples obtained by dividing the thickness
$d$ measured as in Fig. \ref{fig:DR4} by the etching time.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.53j_\perp^{0.79}$ and
    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
\begin{equation}
  \label{eq:etch}
  v=0.53j_\perp^{0.79}
\end{equation}
and
\begin{equation}
  \label{eq:poros}
  p=0.3j_\perp^{0.24},
\end{equation}
where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}

>>>>

In Fig. \ref{fig:JDR}(a) we show the current density
$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
samples $G_1$ and $G_2$, respectively (Eq. \eqref{Eq:J}). We indicate the values
corresponding to positions $A$, $B$, and $C$ on the samples.
In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
selected positions of both samples obtained by dividing the thickness
$d$ measured as in Fig. \ref{fig:DR4} by the etching time.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.68j_\perp^{0.69}$ and
    $p=0.33j_\perp^0.21$, \notaC{cambie las expresiones $v=0.53j_\perp^{0.79}$ 
    and $p=0.3j_\perp^0.24$}
    with corresponding correlation coefficients
      $r_v^2=0.951$ and $r_p^2=0.989$ \notaC{ tambien cambie $r_v^2=0.993$ 
      and $r_p^2=0.0.847$ }(here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
\begin{equation}
  \label{eq:etch}
  v=0.68j_\perp^{0.69} \notaC{cambie v=0.53j_\perp^{0.79}}
\end{equation}
and
\begin{equation}
  \label{eq:poros}
  p=0.33j_\perp^{0.21}, \notaC{cambie p=0.3j_\perp^{0.24}}
\end{equation}
where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.951$
and $r_p^2=0.847$. \notaC{cambie $r_v^2=0.993$
and $r_p^2=0.989$.}
\notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}
